### 2013-11-19 PositionPaper/slaDataInteg.tex
Current state
some rewriting...

\begin{figure}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
\end{figure}

@@

{\color{red}
Here Martin will explain the rewriting problem.
}

>>>>

\begin{figure*}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
\end{figure*}

@@

%{\color{red}
%Here Martin will explain the rewriting problem.
%}

Query rewriting is a well-known problem for the database community.
The problem consists on transforming an abstract query into a set (or list) of lower-level queries to the available databases.
Traditionally, the abstract query is a query over a set of views and the lower-level queries are performed on the available databases whose information compose the view. 
The rewriting is guided by the schema of both abstract and concrete databases.
The answers to the lower level queries are combined in order to obtain the result to be returned to the user.

The query rewriting problem may be generalized to the case of services.
This is a natural consequence of the use of information-providing\footnote{Services that do not perform changes in the data they use.} services as interfaces over relational databases.
Both database queries and service invocations may be represented using a similar syntax.
Indeed, the interfaces to relational databases and information-providing services are exactly the same.
In the case of general services, the abstract query is seen as an abstract service composition, which is rewritten into a \textit{concrete} service composition.
The rewriting process is guided by the interfaces (types) of the abstract and concrete services.

Abstract services and database interfaces have some conspicuous differences.
Services may change information: Two different invocations may not return the same answer, even when given the same input data.
Also service compositions may need to meet some requirements such as QoS or other quality constraints that need to be verified.

Query rewriting techniques have been adapted to the context of service composition~\cite{queryRewriting}. 
In~\cite{UmbertoICWE2013} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting,  known in the database domain.
The proposed approach consists in generating several translations of an abstract service specification into compositions
over concrete  services. 
The solutions proposed are ranked and may be coded into concrete orchestrations.
